On the probability of finding a nonphysical solution through shadowing

### 2020-10-26 main.tex

\begin{figure}\centering
\includegraphics[width=0.48\textwidth]{lorenz_zmax_10_28_2.6666666666666665.png}
\hspace{0.02\textwidth}
\includegraphics[width=0.48\textwidth]{lorenz_zmax2_10_28_2.6666666666666665.png}
\caption{L: the Lorenz map.  The x-axis is the $n$-th local maximum of $u_3(t)$ over a
long solution; the y-axis is the $(n+1)$-th local maximum of $u_3(t)$.  The intersection of this curve
		with the dashed line ($y=x$) indicates the initial condition for the solid line
in Figure \ref{fig:lorenz_periodic}.
R: the Lorenz map iterated twice.  The x-axis is the $n$-th local maximum
of $u_3(t)$; the y-axis is the $(n+2)$-th maximum.  The intersections with the diagonal dashed
line indicate the initial conditions for both the dotted and dashed lines in
Figure \ref{fig:lorenz_periodic}.}
\label{fig:lorenz_map}
\end{figure}
\begin{comment}In Figure 4, the solid line appears only to have one local maximum, which is shown as the fixed point on the left plot of this figure. The two fixed points of the 2-time-iterate of the Lorenz map, shown on the right plot of this figure, both appear to correspond to the local maxima of the dashed curve in Figure 4.\end{comment}
The Lorenz map provides us a tool to find as many periodic solutions as we want.
By intersecting the map with a diagonal line, we can find a local maximum of $u_3(t)$
for which the next maximum is almost the same value.  We then look up the values of
$u_1(t)$ and $u_2(t)$ when $u_3(t)$ achieved this maximum.  This gives us an initial
condition starting from which the solution is nearly periodic.   We can similarly
intersect the second iterate of the Lorenz map (right plot of Figure \ref{fig:lorenz_map},)
and the third iterate, etc, with a diagonal line to find increasingly
complex periodic solutions.

>>>>

\begin{figure}\centering
\includegraphics[width=0.48\textwidth]{lorenz_zmax_10_28_2.6666666666666665.png}
\hspace{0.02\textwidth}
\includegraphics[width=0.48\textwidth]{lorenz_zmax2_10_28_2.6666666666666665.png}
\caption{L: the Lorenz map.  The x-axis is the $n$-th local maximum of $u_3(t)$ over a
long solution; the y-axis is the $(n+1)$-th local maximum of $u_3(t)$.  The intersection of this curve
		with the dashed line ($y=x$) indicates the initial condition for the solid line
in Figure \ref{fig:lorenz_periodic}.
R: the Lorenz map iterated twice.  The x-axis is the $n$-th local maximum
of $u_3(t)$; the y-axis is the $(n+2)$-th maximum.  The intersections with the diagonal dashed
line indicate the initial conditions for both the dotted and dashed lines in
Figure \ref{fig:lorenz_periodic}.}
\label{fig:lorenz_map}
\end{figure}
\nisha{In Figure 4, the solid line appears only to have one local maximum, which is shown as the fixed point on the left plot of this figure. The two fixed points of the 2-time-iterate of the Lorenz map, shown on the right plot of this figure, both appear to correspond to the local maxima of the dashed curve in Figure 4.}
The Lorenz map provides us a tool to find as many periodic solutions as we want.
By intersecting the map with a diagonal line, we can find a local maximum of $u_3(t)$
for which the next maximum is almost the same value.  We then look up the values of
$u_1(t)$ and $u_2(t)$ when $u_3(t)$ achieved this maximum.  This gives us an initial
condition starting from which the solution is nearly periodic.   We can similarly
intersect the second iterate of the Lorenz map (right plot of Figure \ref{fig:lorenz_map},)
and the third iterate, etc, with a diagonal line to find increasingly
complex periodic solutions.
